---
title: "Simple document"
author: "Chhiring Lama"
date: "2024-09-10"
output:
  word_document:
    toc: true
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
  pdf_document:
    toc: true
---
### this on the top is the YAML header

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r eval = FALSE}
samp = rnorm(100)
length(samp)
```

Here eval = false keeps the code but does not run it

```{r echo = FALSE}
samp = rnorm(100)
length(samp)
```

Here echo = false runs it but doesn't give the code that produced it

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`. ###this is inline R code

## Learning Assessment:

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

### Solution:

```{r echo = FALSE, message = FALSE}
##load library
library(tidyverse)
```



```{r message = FALSE}
set.seed(1)

## create a dataframe
example_df <- tibble(
  sample = rnorm(500, mean = 1),
  log_val = sample > 0, 
  abs_val = abs(sample)
  )
```

Here is the preview of first few rows of the dataframe:

```{r message = FALSE}
knitr::kable(head(example_df), format = "markdown")
```


Plot showing the histogram of the absolute value:

```{r warning = FALSE, message = FALSE}
##produce histogram for absolute value
ggplot(example_df, aes(x = abs_val)) +
  geom_histogram()
```

The median value of the absolute value variable is `r format(signif(median(example_df$abs_val), digits = 2), nsmall = 2)`.

# Formatting Text

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

## Learning assessment: 

After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

## Solution:

*   The mean of the random sample is **`r mean(example_df$sample)`**.
*   The median of the random sample is **`r median(example_df$sample)`**.
*   The standard deviation of the random sample is **`r sd(example_df$sample)`**.




